Upper Limits on CN from Falling Evaporating Bodies\\seen towards Beta Pictoris

### 2023-01-04 src/tex/ms.tex
[showyourwork] overleaf sync

%                                                                 aa.dem
% AA vers. 8.2, LaTeX class for Astronomy & Astrophysics
% demonstration file
%                                                       (c) EDP Sciences
%-----------------------------------------------------------------------
%
%\documentclass[referee]{aa} % for a referee version
%\documentclass[onecolumn]{aa} % for a paper on 1 column  
%\documentclass[longauth]{aa} % for the long lists of affiliations 
%\documentclass[rnote]{aa} % for the research notes
%\documentclass[letter]{aa} % for the letters 
%\documentclass[bibyear]{aa} % if the references are not structured 
% according to the author-year natbib style

%
\documentclass{aa}  
\usepackage{graphicx}
\usepackage{rotating}
\usepackage[varg]{txfonts}
\usepackage{txfonts}
\usepackage{color}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{hyperref}
\bibpunct{(}{)}{;}{a}{}{,} % to follow the A&A style

@@

@@

Of all cometary gas emission, the highest signal to noise normally occurs with the CN (0-0) band at $\lambda\simeq 3880$\AA. It is usually the first emission detected in the optical spectrum of a comet as it approaches the Sun, and as been detected in the coma of comets observed at relatively large distances from the Sun {\it e.g.}  \cite{Fitzsimmons1996}. The relative abundance in the coma of most comets of CN/OH$\simeq500$ \citep{AHearn1995}, together with its high fluorescence scattering efficiency factor of $\sim$ 2.6 photons/sec/molecule at 1 au from the Sun and $\dot{r}\simeq 0$ \citep{Schleicher2010}, gives rise to a clear signature of a cometary gas comae. Historically, the CN was believed to be created from photodissociation of HCN, which is present in abundances of the order of 1\% relative to water in cometary ices.  High-spatial resolution sub-mm mapping of HCN distributions supports a nuclear source in some comets \citep{Cordiner 2014}. However, it is now known that in many comets a substantial fraction of CN is released from sub-micron dust grains in the inner coma of comets {\it e.g.} \cite{Fray2005}.

@@

\subsection{UVES observations}
To supplement the HARPS observations, we use 160 epochs of UVES observations obtained between 01 April, 2017 and April 18, 2018 under programme 599.C-0751. The details for these observations are explained in more detail in \cite{vansluijs2019}, and only briefly summarised here. These observations were all obtained using the same instrument setup. We used the standard 437+760 mode of UVES, which uses the \#2 dichroic to allow simultaneous observations in both the red and blue arm. In this mode, the CD\#2 and CD\#4 crossdispersers are used in the blue and red-arm, respectively, providing a simultaneous wavelength coverage of $\sim$3730 $\AA$  to $\sim$5000 $\AA$ in the blue arm, and $\sim$5650 $\AA$ to $\sim$9560 $\AA$ in the red arm. For the remainder of the paper, we will only focus on the data from the blue arm of UVES, as this covers the strong CN band-head seen in Solar system comets. 
For the blue arm, a 0.3''-wide slit was used to obtain the highest possible resolving power ($\sim$90,000 before an intervention on the instrument in October 2017, and $\sim$100,000 after the intervention).

@@

\subsection{Initial data processing}
The data from both instruments was processed in very similar ways. For both datasets, we used the 2d-unmerged echelle spectra, and we treated each order separately. Initially, we aligned all the spectra in the stellar rest-frame using a linear interpolation.

@@

\bibliographystyle{aa}
\bibliography{febspec.bib}

>>>>

%                                                                 aa.dem
% AA vers. 8.2, LaTeX class for Astronomy & Astrophysics
% demonstration file
%                                                       (c) EDP Sciences
%-----------------------------------------------------------------------
%
%\documentclass[referee]{aa} % for a referee version
%\documentclass[onecolumn]{aa} % for a paper on 1 column  
%\documentclass[longauth]{aa} % for the long lists of affiliations 
%\documentclass[rnote]{aa} % for the research notes
%\documentclass[letter]{aa} % for the letters 
%\documentclass[bibyear]{aa} % if the references are not structured 
% according to the author-year natbib style
\documentclass{aa}  
\usepackage{rotating}
\usepackage{natbib}
\usepackage{amsmath}
\bibpunct{(}{)}{;}{a}{}{,} % to follow the A&A style

\usepackage{color}
\usepackage{hyperref}
\hypersetup{colorlinks=true,allcolors=[rgb]{0,0,0.8}}

@@

% the three lines suppress the hyperref 'link empty' warnings
% explanation at: https://tex.stackexchange.com/questions/345764/journal-class-shows-package-hyperref-warning-suppressing-link-with-empty-targe
\makeatletter
\renewcommand*\aa@pageof{, page \thepage{} of \pageref*{LastPage}}
\makeatother

@@

Of all cometary gas emission, the highest signal to noise normally occurs with the CN (0-0) band at $\lambda\simeq 3880$\AA. It is usually the first emission detected in the optical spectrum of a comet as it approaches the Sun, and as been detected in the coma of comets observed at relatively large distances from the Sun {\it e.g.}  \cite{Fitzsimmons1996}. The relative abundance in the coma of most comets of CN/OH$\simeq500$ \citep{AHearn1995}, together with its high fluorescence scattering efficiency factor of $\sim$ 2.6 photons/sec/molecule at 1 au from the Sun and $\dot{r}\simeq 0$ \citep{Schleicher2010}, gives rise to a clear signature of a cometary gas comae. Historically, the CN was believed to be created from photodissociation of HCN, which is present in abundances of the order of 1\% relative to water in cometary ices.  High-spatial resolution sub-mm mapping of HCN distributions supports a nuclear source in some comets \citep{Cordiner2014}. However, it is now known that in many comets a substantial fraction of CN is released from sub-micron dust grains in the inner coma of comets {\it e.g.} \cite{Fray2005}.

@@

\subsection{UVES observations}
To supplement the HARPS observations, we use 160 epochs of UVES observations obtained between 01 April, 2017 and April 18, 2018 under programme 599.C-0751.
%
The details for these observations are explained in more detail in \cite{vansluijs2019}, and summarised here.
%
These observations were all obtained using the same instrument setup.
%
We used the standard 437+760 mode of UVES, which uses the \#2 dichroic to allow simultaneous observations in both the red and blue arm.
%
In this mode, the CD\#2 and CD\#4 cross-dispersers are used in the blue and red-arm, respectively, providing a simultaneous wavelength coverage of $\sim$3730 $\AA$  to $\sim$5000 $\AA$ in the blue arm, and $\sim$5650 $\AA$ to $\sim$9560 $\AA$ in the red arm.
%
For the remainder of the paper, we will only focus on the data from the blue arm of UVES, as this covers the strong CN band-head seen in Solar system comets.
%
For the blue arm, a 0.3''-wide slit was used to obtain the highest possible resolving power ($\sim$90,000 before an intervention on the instrument in October 2017, and $\sim$100,000 after the intervention).

@@

\subsection{Initial data processing}
The data from both instruments was processed in similar ways.
%
For both datasets, we used the 2d-unmerged echelle spectra, and we treated each order separately.
%
All the spectra were transformed into the stellar rest-frame using linear interpolation.

The number of observations varies from night to night, from a few spectra to over a hundred.
%
An average of all the spectra in one night was made for all the nights of observations.

The blaze function dominates the flux profile of the spectra.
%
One of the nights with a high signal to noise was chosen to act as an initial estimate for the blaze function: this spectrum was binned in the spectral direction to remove both narrow absorption lines and the rotationally broadened stellar chromospheric lines, but preserve the shape of the blaze function.
%
A low order second or third order polynomial was fit to each echelle order, and this fit spectrum served as a blaze function estimate.

For all the spectra in a given night:
 - Divide the spectrum by the reference spectrum, which hs the fit of the low order polynomial to the best night spectrum.
 - Combine all these spectrum within a single night all together, to form the final night spectrum (this still has the BLAZE function in it...)

 For all the night spectra:

 We median combine all the nights together.

 Bin the spectrum and clip it, interpolate using a cubic spline.

 Divide this interpolated cubic spline into each of the nightly spectra.

THis removes the blaze function, but there remain low spatial frequency variations between different nights, due to the changing slit illumination as the star moves across the spit aperture.

We then fit a second order polynomial to each individual night and divide this out, resulting in a flattened spectrum for each night.

@@

\bibliographystyle{aa}
\bibliography{bib.bib}
